ms2

### 2017-08-16 ms2/ms2_display.Rmd
ms2 coefficient correlations

>>>>

## Comparing the predictive power of mean consumption and fraction nonzero

How do the regressions $R \sim f_>$ compare to $R \sim \mu$? Here I look at the correlation between the coefficients $\beta_\mu$ and $\beta_{f_>}$ across bug/drug combinations. The correlation is really high for HRRs and just regular high for states.

```{r univariate_result_correlation}
results %>%
  filter(str_detect(model, '^uni'), term != '(Intercept)') %>%
  select(unit_type, bug, drug_group, term, estimate) %>%
  spread(term, estimate) %>%
  group_by(unit_type) %>%
  summarize(cor_between_betas=cor(fnz, mean)) %>%
  kable
```

In other words, if you do the regression with $f_>$, you can predict with very high accuracy the coefficient from the univariate regression on $\mu$.
